\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-06-23 Papers/ViscousInstabilities/article_figure1.tex
updates on progress

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[h]
\centering
\vbox{\includegraphics[width=.5\textwidth]{./Pics/element_n.pdf}}
\caption{This is a graphical representation of two different element types. Element A is the \PN[1]{2}, while element B is the \PN[1]{1}. Porosity $\phi_{i}$ and permeability $K_{i}$ are CV-wise quantities, whereas velocity and pressure are primarily represented in FE space. Scalar fields (such saturation, density, viscosity etc) are also represented in CV space.}
}
\label{fig:fem_elem}
\end{figure}

@@

%%%%
%%%%  FIGURE 4
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{-0.3cm}
\includegraphics[width=.8\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_perm_1.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) map of permeabilities ($\mathbf{K}$)
}
\vspace{0.25cm}
\hbox{\hspace{1.5cm}
\includegraphics[width=.65\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_250_2.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=250  \red{(Is this time or the vtu number ??)}
}
\vspace{0.25cm}
\hbox{\hspace{1.5cm}
\includegraphics[width=.65\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_3000_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (c) flow at t=3000  
}
}     
\caption{Model validation of fluid displacement in heterogeneous porous media: (a) the domain is divided into four subdomains with prescribed synthetic permeability, $\mathbf{K}_{1}=1$ and $\mathbf{K}_{2}=2.5$; (b-c) snapshots of saturation (displacing fluid) field at \red{t=XX} and \red{t=XX}. The domain is discretised in \red{XX} \PN[1]{2} elements. \red{(ALSO YOU MUST ADD SATURATION LEGENDS IN ALL FIGURES.)}}
\label{fem_cv_represent_a}
\end{figure}
\clearpage

>>>>

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[h]
\centering
\vbox{\includegraphics[width=.75\textwidth]{./Pics/element_n.pdf}}
\caption{This is a graphical representation of two different element types. Element A is the \PN[1]{2}, while element B is the \PN[1]{1}. Porosity $\phi_{i}$ and permeability $K_{i}$ are CV-wise quantities, whereas velocity and pressure are primarily represented in FE space. Scalar fields (such saturation, density, viscosity etc) are also represented in CV space.}
\label{fig:fem_elem}
\end{figure}
\clearpage

@@

%%%%
%%%%  FIGURE 4
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{-0.3cm}
\includegraphics[width=.8\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_perm_1.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) map of permeabilities ($\mathbf{K}$)
}
\vspace{0.25cm}
\hbox{\hspace{1.5cm}
\includegraphics[width=.9\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_250_2.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=250  
}
\vspace{0.25cm}
\hbox{\hspace{1.5cm}
\includegraphics[width=.65\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_3000_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (c) flow at t=3000  
}
}     
\caption{Model validation of fluid displacement in heterogeneous porous media: (a) the domain is divided into four subdomains with prescribed synthetic permeability, $\mathbf{K}_{1}=1$ and $\mathbf{K}_{2}=2.5$; (b-c) snapshots of saturation (displacing fluid) field at $t=250$ and $t=3000$ sec. The domain is discretised in $5960$ \PN[1]{2} elements. }
\label{fem_cv_represent_a}
\end{figure}
\clearpage
